The Impact of Cloud Computing in $10$ Years

### 2013-05-05 essay/tex/essay.tex
finish education section in essay.

Event if cloud computing had achieved so many advantages all over these years, we may notice that the current stage of cloud computing has influenced very limited industries, most of them are concentrated in Internet or Web related businesses. Two major use of the cloud infrastructure are application host and storage service. However, the

\section{Mobile and Cloud Computing}

@@

Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy.

@@

On the other hand, fortunately, many startups have started to build such a system under the schools' needs. Each individual product can be used by different schools and students that all of them actually share the same system. The products like eBackpack or edmodo are almost free to everyone to use or small amount of fee is charged, which definitely can reduce the cost for the schools to replace the old system. Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their service or product at their lowest cost.

In addition to the lower level education system, the cloud computing also benefits the higher education system.

\section{Online-to-Offline Business and Cloud Computing}

\section{Scientific Computing and Cloud Computing}

>>>>

Event if cloud computing had achieved so many advantages all over these years, we may notice that the current stage of cloud computing has influenced very limited industries, most of them are concentrated in Internet or Web related businesses. However, we think the cloud computing could power more industries in the next $10$ year.

\section{Mobile and Cloud Computing}
The reason I first discuss the mobile technology and cloud computing is simply because I have observed the trend of the commercial electronics. Smartphones, tablets and ultra-books are becoming more and more popular in recent several years. Android and iOS powered devices attracts much more attentions than a PC or laptop. These devices are highly mobile, equipped with high quality camera and GPS which make the device a central hub for the multiple other equipment like camera or GPS navigators. Additionally, the Android and iOS app eco-system have made the smartphones much more valuable than a simple phone. We can see people playing Angry Birds when they are taking a bus and listening to the music when they are exercising. The whole category of educational apps confirm me the significance of smart devices on education. Therefore, it is reasonable to see the trends of mobile devices could somehow dominate the market in the future.

Interestingly, if we look at the app stores, you can always see the shadows of cloud computing. I say ``shadow'' because there is not too many devices directly claim they belongs to cloud computing. But many of them use cloud computing heavily as their background support. For example, the new private social network app Path\cite{path} provides excellent social network experience via smartphones with close friends and families. Their backend systems such as data storage, machine learning/data mining and message exchanges undoubtedly depend on Amazon AWS infrastructure. Another example is the intelligent social media reader Prismatic\cite{prismatic} on smarthpones. This reader learns the user's interests and topics among numerous posts and streams online, then it starts filtering the news and presents the most relevant news to the users. Prismatic's app on the smartphone is very simple, but the backend systems also rely on Amazon AWS because it has to deal with large scale machine learning and realtime data service. These two components require super powerful computation power, reliable data storage and scalable front-end service, which is hard for a startup to build from the scratch.

Furthermore, some challenges in the mobile computing are still unresolved. For example, the mobile network latency and battery issues which are critical to the fluency of mobile applications. To cope with the issues, some researchers propose the concept of \emph{Cloudlets}~\cite{satyanarayanan2009case} which bridges the mobile devices and the clouds through a middle station. To deal with the battery issues, some researchers proposes the \emph{offloading}~\cite{kumar2010cloud} techniques to transfer the computation from the mobile devices to the cloud. To speed up the mobile web browsing experience, Chrome patches the cloud speeding techniques by prefetching web pages in Google's cloud to speed up the webpage loading speed on the mobile devices. Therefore, we could see the cloud computing is not only a back-end supporter but a key to solve problems in mobile computing as well.

@@

Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy in the next $10$ years.

@@

On the other hand, fortunately, many startups have started to build such a system under the schools' needs. Each individual product can be used by different schools and students that all of them actually share the same system. The products like eBackpack or edmodo are almost free to everyone to use or small amount of fee is charged, which definitely can reduce the cost for the schools to replace the old system. Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their service or product at their lowest cost. For example, Amazon AWS and Google App Engine are the most popular service providing environment for many startups.

Therefore, it is possible to expect that many companies, especially startups, could join the business to provide cheap and convenient education service in cloud to the majority of schools.

In addition to the primary and secondary education system, the cloud computing also benefits the higher education system. Universities already have some basic infrastructure deployed in clouds. For example, the \emph{volmail} system in UT will be upgraded into Microsoft's Office365 platform which is Microsoft's in-cloud office software system. However, the cloud computing's impact in universities are not limited in IT infrastructure.

Massive open online courseware (MOOC) has become a hot area in higher education recently. Typical companies like Coursera provides open and free online classes to students around the world. According to an answer from a Coursera's engineer on Quora\cite{quora2coursera}, their site relies heavily on Amazon AWS platform because each online course usually contains many videos and need a scalable student interaction platform. What coursera can bring to a student now is the accessibility to many different courses from various universities even if the students' universities do not open such a course. For example, I am taking Natural Language Processing and Probabilistic Graphic Model courses on Coursera because we do not have such courses in UT. But, in my opinion, MOOC is changing the way students learn knowledge.

First, the students can arrange the lecture time by himself within a week so that the time does not conflict with their courses at school. Second, many more students register the class at once, then the analysis will give more accurate information on how well the student performs. Third, the professors can experiment teachings in a more flexible ways, for instance, the students can review other's assignments or projects instead of the professor himself. Fourth, the students can access the course materials anywhere instead of being limited in the classroom.

However, my viewpoint does not necessarily mean the MOOC will replace university some day. In contrast, I would say never. One important phase in learning is the interactions between students and professors. Even if MOOC can provide the platform for such an interaction (not a big problem in cloud computing), the reality is that one or two professors cannot handle thousands of students at a time. Therefore, MOOC could be a good learning makeups in higher education to enjoy different teaching styles and viewpoints. Besides, the open source MOOC platform Class2Go\cite{class2go} makes it much easier for anyone who wants to make an online course for others.

\section{Online-to-Offline Business and Cloud Computing}
Another part of the cloud computing's influence in the next $10$ years could be the business, especially the small business. If we look at the small busin
